Casual Bandits

### 2016-01-31 causal-bandit/icml-2015/discussion.tex
some explaination of general case, changes to earlier sections to improve flow to general case
moved stuff into more relevent places

\section{Future Open Questions}
\begin{itemize}
\item Known but arbitrary structure
\item Learning structure then exploiting
\end{itemize}
\section{Conclusion}

>>>>

\cite{wu2015online} consider a relevant feedback model.

\section{Future Open Questions}

\subsection{General graphs with known structure but latent variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.

\subsection{Graphs with partially or unknown structure}

\begin{itemize}

\item Partially known structure
There has been substantial work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class \cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014}. This problem arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. Key results $bigo(n)$ singleton or $bigo(log log n)$ multi-variate experiments are required.
- Focus on minimizing the number of experiments that must be performed. Examples of active versus online learning. The cost of experiments constant or at least known.

\item Unknown Structure
If we need to learn the structure, in an online environment. 
Experiment is much, much more revealing than inference from observational data. We would expect it to dominate.

\end{itemize}
\section{Conclusion}
